---
title: "Planting Summary"
author: "Darla Knuth"
date: "2025-01-28"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(tidyverse)
library(ggplot2)
library(RColorBrewer)
library(kableExtra)
library(DT)
```
# Summary of Planter Monitor Data {.tabset}

## Planting 2.2

```{r include=FALSE}
planting_file <- read.csv("planting_2.2.csv")

planting_file <- planting_file %>% 
  separate(Date...Time, c("Date","Time","PM"), sep = " ")


```

```{r include=FALSE}

time <- planting_file %>% 
  group_by(Date) %>% 
  summarise(
    min=min(Time),
    max=max(Time))
  
  
```

### Planting Start and End Times

```{r echo=FALSE}
kable(time,
      col.names = c("Date","Start Time", "End Time"))
```

```{r include=FALSE}
Rows <- planting_file %>%
  select(c("Date", "Time","Range", "RowA","RowB","RowC","RowD")) %>% 
  pivot_longer(cols = starts_with("Row"),
               names_to = "Row",
               names_prefix = "Row",
               values_to = "Row_number",
               values_drop_na = TRUE)

Counts <- planting_file %>% 
  select(c("Date","Time","Range","CountA","CountB","CountC","CountD")) %>% 
   pivot_longer(cols = starts_with("Count"),
               names_to = "Row",
               names_prefix = "Count",
               values_to = "Count",
               values_drop_na = TRUE)

Skips <- planting_file %>% 
  select(c("Date","Time","Range","SkipA","SkipB","SkipC","SkipD")) %>% 
   pivot_longer(cols = starts_with("Skip"),
               names_to = "Row",
               names_prefix = "Skip",
               values_to = "Skip",
               values_drop_na = TRUE)

Doubles <- planting_file %>% 
  select(c("Date","Time","Range","DoubleA","DoubleB","DoubleC","DoubleD")) %>% 
   pivot_longer(cols = starts_with("Double"),
               names_to = "Row",
               names_prefix = "Double",
               values_to = "Double",
               values_drop_na = TRUE)
```

```{r include=FALSE}
long_planting <- Rows %>% 
  right_join(Counts)%>% 
  right_join(Skips)%>% 
  right_join(Doubles)

long_planting <- long_planting[,c(1,2,4,3,5:8)]

```

### Seed Counts, Skips, and Doubles by Nursery Row

```{r echo=FALSE}
DT::datatable(long_planting, 
              colnames = c("Row Number" = "Row_number"),
              caption = htmltools::tags$caption(
    style = 'caption-side: bottom; text-align: center;',
    'Table 1: ', htmltools::em('Planter unit data by range and row')),
    filter = 'top')
```

```{r include=FALSE}
summary_table <- long_planting %>% 
  group_by(Row) %>% 
  filter(Row_number != 13 & Row_number != 25 & Row_number != 37) %>% 
  summarise(
    `Average Seed Count` = round(mean(Count),2),
    `Average Skips` = round(mean(Skip),2),
    `Average Double` = round(mean(Double),2),
    `Total Seed Count` = sum(Count),
    `Total Skips` = sum(Skip),
    `Total Doubles` = sum(Double),
    ) %>% 
  rename(
    `Planter Unit` = Row
  )
```

### Performance of Planter by Planter Unit

```{r echo=FALSE}
DT::datatable(summary_table,
              caption = htmltools::tags$caption(
    style = 'caption-side: bottom; text-align: center;',
    'Table 2: ', htmltools::em('Summary of planter performance by unit')))  
```

### Planting Shifts and Errors

##### Fill shows seed count per plot

```{r echo=FALSE}
heat_map <- long_planting %>% 
  select(c("Range", "Row_number","Count")) %>% 
  arrange(Row_number, Range)

heat_map <- heat_map %>% 
  pivot_wider(names_from = Row_number, values_from = Count) %>% 
  arrange(Range)


heat_test <- data.matrix(heat_map)

par(xpd=TRUE,mai = c(0,0,0,0))

heatmap(as.matrix(heat_map[, -1]), Rowv = NA, Colv = NA,
        xlab = "Row", ylab = "Range",
        col= brewer.pal(11,"RdYlGn"))

legend(0,0.9, legend=c("Low", "", "","", "", "Avg","", "", "","", "High"), 
     fill=brewer.pal(11,"RdYlGn"), bty="n")
           

```

## Planting 2.3

```{r include=FALSE}
planting_file <- read.csv("planting_2.3.csv")

planting_file <- planting_file %>% 
  separate(Date...Time, c("Date","Time","PM"), sep = " ")


```

```{r include=FALSE}

time <- planting_file %>% 
  group_by(Date) %>% 
  summarise(
    min=min(Time),
    max=max(Time))
  
  
```

### Planting Start and End Times

```{r echo=FALSE}
kable(time,
      col.names = c("Date","Start Time", "End Time"))
```

```{r include=FALSE}
Rows <- planting_file %>%
  select(c("Date", "Time","Range", "RowA","RowB","RowC","RowD")) %>% 
  pivot_longer(cols = starts_with("Row"),
               names_to = "Row",
               names_prefix = "Row",
               values_to = "Row_number",
               values_drop_na = TRUE)

Counts <- planting_file %>% 
  select(c("Date","Time","Range","CountA","CountB","CountC","CountD")) %>% 
   pivot_longer(cols = starts_with("Count"),
               names_to = "Row",
               names_prefix = "Count",
               values_to = "Count",
               values_drop_na = TRUE)

Skips <- planting_file %>% 
  select(c("Date","Time","Range","SkipA","SkipB","SkipC","SkipD")) %>% 
   pivot_longer(cols = starts_with("Skip"),
               names_to = "Row",
               names_prefix = "Skip",
               values_to = "Skip",
               values_drop_na = TRUE)

Doubles <- planting_file %>% 
  select(c("Date","Time","Range","DoubleA","DoubleB","DoubleC","DoubleD")) %>% 
   pivot_longer(cols = starts_with("Double"),
               names_to = "Row",
               names_prefix = "Double",
               values_to = "Double",
               values_drop_na = TRUE)
```

```{r include=FALSE}
long_planting <- Rows %>% 
  right_join(Counts)%>% 
  right_join(Skips)%>% 
  right_join(Doubles)

long_planting <- long_planting[,c(1,2,4,3,5:8)]

```

### Seed Counts, Skips, and Doubles by Nursery Row

```{r echo=FALSE}
DT::datatable(long_planting, 
              colnames = c("Row Number" = "Row_number"),
              caption = htmltools::tags$caption(
    style = 'caption-side: bottom; text-align: center;',
    'Table 1: ', htmltools::em('Planter unit data by range and row')),
    filter = 'top')
```

```{r include=FALSE}
summary_table <- long_planting %>% 
  group_by(Row) %>% 
  summarise(
    `Average Seed Count` = round(mean(Count),2),
    `Average Skips` = round(mean(Skip),2),
    `Average Double` = round(mean(Double),2),
    `Total Seed Count` = sum(Count),
    `Total Skips` = sum(Skip),
    `Total Doubles` = sum(Double),
    ) %>% 
  rename(
    `Planter Unit` = Row
  )
```

### Performance of Planter by Planter Unit

```{r echo=FALSE}
DT::datatable(summary_table,
              caption = htmltools::tags$caption(
    style = 'caption-side: bottom; text-align: center;',
    'Table 2: ', htmltools::em('Summary of planter performance by unit')))  
```

### Planting Shifts and Errors

##### Fill shows seed count per plot

```{r echo=FALSE}
heat_map <- long_planting %>% 
  select(c("Range", "Row_number","Count")) %>% 
  arrange(Row_number, Range)

heat_map <- heat_map %>% 
  pivot_wider(names_from = Row_number, values_from = Count) %>% 
  arrange(Range)



heat_test <- data.matrix(heat_map)

par(xpd=TRUE,mai = c(0,0,0,0))

heatmap(as.matrix(heat_map[, -1]), Rowv = NA, Colv = NA,
        xlab = "Row", ylab = "Range",
        col= brewer.pal(11,"RdYlGn"))

legend(0,0.9, legend=c("Low", "", "","", "", "Avg","", "", "","", "High"), 
     fill=brewer.pal(11,"RdYlGn"), bty="n")

```